---
title: "Shiny Application and Reproducible Pitch"
author: "Jie Li"
date: "July 17, 2018"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
The Mtcars Plotter is an plotting tool for an exploratory data analysis of the mtcars data set in R. It allows you display diffrent dimensions of the dataset and plot it agains an axis of choice. Furthermore you can display a smoother and facet the rows and columns.

1. mpg Miles/(US) gallon
2. cyl Number of cylinders
3. disp Displacement (cu.in.)
4. hp Gross horsepower
5. drat Rear axle ratio
6. wt Weight (1000 lbs)
7. qsec ¼ mile time vs V/S
8. am Transmission (0 = automatic, 1 = manual)
9. gear Number of forward gears
10. carb Number of carburetors

## Recommendation

The program is represting using shiny presentation.
The testing setup are suggested as:

Sample size:30

X=mpg

Y=hp

Color=wt

Facet colum=am

Facet row=none

Smooth =T

## R Output

```{r}
library(shiny)
library(ggplot2)
dataset <- mtcars
inputPanel(
          sliderInput('sampleSize', 'Sample Size', min=10, max=nrow(dataset),
                      value=min(20, nrow(dataset)), step=5, round=0),
          selectInput('x', 'X', names(dataset)),
          selectInput('y', 'Y', names(dataset), names(dataset)[[4]]),
          selectInput('color', 'Color', c('None', names(dataset))),
          # checkboxInput('jitter', 'Jitter'),
          checkboxInput('smooth', 'Smooth'),
          selectInput('facet_row', 'Facet Row', c(None='.', names(dataset))),
          selectInput('facet_col', 'Facet Column', c(None='.', names(dataset)))
)


renderPlot({
       dataset <- reactive( {
          mtcars[sample(nrow(mtcars), input$sampleSize),]
     })

     

          p <- ggplot(dataset(), aes_string(x=input$x, y=input$y)) + geom_point()

          if (input$color != 'None')
               p <- p + aes_string(color=input$color)

          facets <- paste(input$facet_row, '~', input$facet_col)
          if (facets != '. ~ .')
               p <- p + facet_grid(facets)

          # if (input$jitter)
          #      p <- p + geom_jitter()
          if (input$smooth)
               p <- p + geom_smooth()
          print(p)
},height = 200,width = 400)

```


## Thank you

